\cvsection{Teaching Experience}
\begin{cventries}
	\cventry
	{Physical Chemistry Tutor}
	{University of Bath}
	{BATH, UK}
	{SEPT. 2015 - PRESENT}
	{
		\begin{cvitems}
			\item {Running physical chemistry tutorials for first year natural sciences undergraduate students}
			%\item {Covering topics including intermolecular forces, kinetics, spectroscopy, and thermodynamics.}
			\item {Pioneered the use of Jupyter Notebooks in tutorials to both aid in the students understanding}
		\end{cvitems}
	}
	\cventry
	{Computational Laboratory Demonstrator}
	{}
	{}
	{JAN. 2016 - PRESENT}
	{
		\begin{cvitems}
			\item {Demonstrated first and second year undergraduate computational chemistry laboratory exercises, particularly focussing on introducing Python programming}
			\item {Helped to develop laboratory exercises to develop skills in Microsoft Excel, an understanding of classical molecular dynamics simulations, and to introduce Python programming for data analysis}
		\end{cvitems}
	}
	\cventry
	{Mathematics for Chemistry Lecturer}
	{}
	{}
	{SEPT. 2016 - MAR. 2017}
	{
		\begin{cvitems}
			\item {Delivery of workshops in fundemental mathematical concepts for chemists, ensuring that all chemistry first year students had consistent mathematical background}
		\end{cvitems}
	}
	\cventry
	{X-ray \& Neutron Techniques for Chemists Lecturer}
	{}
	{}
	{JAN. 2016 - PRESENT}
	{
		\begin{cvitems}
			\item {Delivery of workshops devoted to the analysis of small angle scattering and reflectometry as a component of a final year undergraduate course}
		\end{cvitems}
	}
	\cventry
	{Introduction to Unix \& Programming Lecturer and Demonstrator}
	{}
	{}
	{FEB. 2018 - DEC. 2018}
	{
		\begin{cvitems}
			\item {Twice assisted in the delivery of a practical workshop designed to introduce PhD student from through-out the university of Unix and programming}
			\item {Included leading the "Introduction of Python" workshop, based on Software Carpentry materials}
		\end{cvitems}
	}
	\cventry
	{Lecturer}
	{ISIS Neutron Training Course}
	{HARWELL-OXFORD, UK}
	{MAR. 2017 - PRESENT}
	{
		\begin{cvitems}
			\item {Twice invited to lecture at the ISIS Neutron Training Course}
			\item {Developed and delivered a one hour lecture introducing classical molecular dynamics simulations and showing how they can be applied to neutron scattering}
			\item {Further prepared in interactive tutorial presenting how molecular dynamics simulation could be applied to the analysis of neutron reflectometry data}
		\end{cvitems}
	}
	\cventry
	{Demonstrator}
	{SASSIE Training Course}
	{VARIOUS, UK}
	{MAR. 2017 - PRESENT}
	{
		\begin{cvitems}
			\item {Aided in the demonstration of the SASSIE biological small angle scattering package at training events for PhD students and Postdocs}
		\end{cvitems}
	}
	\cventry
	{Contributor}
	{\href{http://pythoninchemistry.org}{pythoninchemistry.org}}
	{BATH, UK}
	{NOV. 2017 - PRESENT}
	{
		\begin{cvitems}
			\item {Webmaster and contributor to the pythoninchemistry web resource}
			\item {Resource designed to introduce chemistry students to aspects of programming, using Python and Jupyter Notebooks}
			\item {Developing teaching resources that introduce my basic concepts from programming, such as functions, loops, and plotting}
		\end{cvitems}
	}
\end{cventries}
